### 2023-01-29 README.Rmd
make Readme display better
Change the function name to `dockerize` before it's too late
add logo
Fix #12

# gran

@@

```r
make_docker(graph, "~/rocker_test")
```

@@

>>>>

# gran <img src="man/figures/gran_logo.svg" align="right" height="200" />

@@

```r
dockerize(graph, "~/rocker_test")
```

@@

## Using alternative Rocker images

One can also select other Rocker versioned images: `rstudio`, `tidyverse`, `verse`, `geospatial`.

```r
dockerize(graph, "~/rocker_test", image = "rstudio")
```

`tidyverse`, `verse`, and `geospatial` are similar to the default (`r-ver`). For `rstudio`, one needs to build and launch it with:

```bash
cd ~/rocker_test
sudo docker build -t gran .
sudo docker run -p 8787:8787 -e PASSWORD=abc123 --rm --name "grantest" -ti gran
```

With any browser, go to: `local:8787`. The default username is `rstudio`, password is as specified.

## Acknowledgment

The logo of gran is a remix of [this](https://commons.wikimedia.org/wiki/File:Flag_of_the_Canary_Islands.svg) public domain image.
